### 2020-04-27 Temp_tables/Tables_paper/01_Paper_version_1/table_8.tex
back up before new paper

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{booktabs,caption,threeparttable, siunitx, adjustbox}

@@

%%% Table 1
\begin{table}[!htbp] \centering
  \caption{SO2 reduction during the subsequent FYP}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{lrrrr}
      \toprule
      {} & \multicolumn{2}{l}{Failure} & \multicolumn{1}{l}{Success} \\
      \hline
      &      (1998-2000) & (2001-2005) &  (2006-2010) \\
      \midrule
      \textbf{TCZ} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -     & -14\% &   \\
      \text{\footnotesize{SO2 \% reduction}} & -7\% & 38\%  & -15\%     &   \\

      \textbf{No TCZ} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -     & -4\%  &   \\
      \text{\footnotesize{SO2 \% reduction}} & 21\%  & 64\%  & -11\%     &   \\

      \textbf{All sample} & & & \\
      \text{\footnotesize{SO2 target}}       & -     & -10\% & -10\% &   \\
      \text{\footnotesize{SO2 \% reduction}} & -2\%     & 45\%  & -13\% &   \\

      \bottomrule
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Sources: Author's own computation \\
      The list of TCZ is provided by the State Council, 1998. "Official Reply to the State Council Concerning Acid Rain Control Areas and Sulfur Dioxide Pollution Control Areas". The information about the SO2 level are collected using various edition of the China Environment Statistics Yearbook. We compute the reduction of SO2 emission using the same methodology as Chen and al.(2018). 
    \end{tablenotes}
\end{table}

\hfill \break

%%% Table 2

\begin{table}[!htbp] \centering
    \caption{Summary Statistics by city-industry and city characteristics}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{lrrrr}
      \multicolumn{1}{l}{\textbf{\small Panel A: City/city-industry characteristics}} \\
      \toprule
      & \multicolumn{2}{l}{No TCZ} & \multicolumn{2}{l}{TCZ} \\
      {}                         & mean   & std    & mean   & std    \\
      \midrule
      SO2_{ikt}                  & 182873 & 372028 & 174308 & 357225 \\
      \text{count share SOE}_k   & 0.093  & 0.094  & 0.082  & 0.086  \\
      \text{output share SOE}_k  & 0.147  & 0.153  & 0.136  & 0.151  \\
      \text{capital share SOE}_k & 0.220  & 0.197  & 0.209  & 0.198  \\
      \text{labour share SOE}_k  & 0.188  & 0.162  & 0.176  & 0.162  \\
      \text{output}_{kit}        & 0.028  & 0.101  & 0.058  & 0.266  \\
      \text{capital}_{kit}       & 0.008  & 0.030  & 0.014  & 0.054  \\
      \text{labour}_{kit}        & 0.009  & 0.024  & 0.016  & 0.056  \\
      \bottomrule
      \\ %%% Create second table
      \multicolumn{1}{l}{\textbf{\small Panel B: SO2 emission by city-location}} \\
      \toprule
      {} & \multicolumn{2}{l}{\footnotesize difference (10.000 tons units)} & \multicolumn{2}{l}{variance (\footnotesize \%)} \\
                  & No TCZ   & TCZ      & No TCZ & TCZ  \\
      Location    &          &          &        &      \\
      \midrule
      Full sample &    -192 & -436 &     0.22 & 0.26 \\
      Central     &    -238 & -232 &     0.25 & 0.19 \\
      Coastal     &    -138 & -659 &     0.12 & 0.29 \\
      Northeast   &    -206 &  -89 &     0.30 & 0.08 \\
      Northwest   &    -115 & -277 &     0.21 & 0.31 \\
      Southwest   &    -272 & -503 &     0.31 & 0.29 \\
      Non Coastal &    -215 & -302 &     0.28 & 0.23 \\
      Coastal     &    -140 & -578 &     0.13 & 0.28 \\
      \bottomrule
      \hline
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item Panel A provides summary statistics for the main variables used in the subsequent empirical analysis. \\
      Panel B provides summary statistics for the SO2 emission (in 10.000 tons) for Chinese cities (228), split into TCZ (140) and non-TCZ (88) cities
      \\
      Sources: Author's own computation
    \end{tablenotes}
\end{table}

\hfill \break

%%% Table 3
\begin{table}[!htbp] \centering
  \caption{Soft budget constraint as reflected in the SOEs’ reaction to the TCZ policy in China: Baseline result}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\
      \cline{2-5}
      \\[-1.8ex] & (1) & (2) & (3) & (4)\\
      \hline \\[-1.8ex]
      output_{ikt}                                                                            & $-$0.058       & $-$0.059        & $-$0.059        & $-$0.059        \\
                                                                                              & (0.114)        & (0.114)         & (0.114)         & (0.113)         \\
      capital_{ikt}                                                                           & 0.922$^{*}$    & 0.929$^{*}$     & 0.933$^{**}$    & 0.937$^{**}$    \\
                                                                                              & (0.479)        & (0.476)         & (0.475)         & (0.474)         \\
      labour_{ikt}                                                                            & 1.550          & 1.550           & 1.545           & 1.538           \\
                                                                                              & (1.024)        & (1.023)         & (1.023)         & (1.021)         \\
      TCZ_i \times \text{Polluted}_k \times \text{Period}                                     & $-$0.259       & $-$0.298$^{**}$ & $-$0.336$^{**}$ & $-$0.377$^{**}$ \\
                                                                                              & (0.160)        & (0.142)         & (0.154)         & (0.154)         \\
      TCZ_i \times \text{count share SOE}_{k} \times \text{Period}                            & $-$1.235$^{*}$ &                 &                 &                 \\
                                                                                              & (0.709)        &                 &                 &                 \\
      TCZ_i \times \text{Polluted}_k \times \text{count share SOE}_{k} \times \text{Period}   & 1.565$^{*}$    &                 &                 &                 \\
                                                                                              & (0.910)        &                 &                 &                 \\
      TCZ_i \times \text{output share SOE}_{k} \times \text{Period}                           &                & $-$0.824        &                 &                 \\
                                                                                              &                & (0.515)         &                 &                 \\
      TCZ_i \times \text{Polluted}_k \times \text{output share SOE}_{k} \times \text{Period}  &                & 1.315$^{**}$    &                 &                 \\
                                                                                              &                & (0.609)         &                 &                 \\
      TCZ_i \times \text{capital share SOE}_{k} \times \text{Period}                          &                &                 & $-$0.682$^{*}$  &                 \\
                                                                                              &                &                 & (0.399)         &                 \\
      TCZ_i \times \text{Polluted}_k \times \text{capital share SOE}_{k} \times \text{Period} &                &                 & 1.065$^{**}$    &                 \\
                                                                                              &                &                 & (0.513)         &                 \\
      TCZ_i \times \text{labour share SOE}_{k} \times \text{Period}                           &                &                 &                 & $-$1.020$^{**}$ \\
                                                                                              &                &                 &                 & (0.518)         \\
      TCZ_i \times \text{Polluted}_k \times \text{labour share SOE}_{k} \times \text{Period}  &                &                 &                 & 1.532$^{**}$    \\
                                                                                              &                &                 &                 & (0.598)         \\
      \hline \\[-1.8ex]
      city-year fixed effects                                                                 & Yes            & Yes             & Yes             & Yes             \\
      Industry-year fixed effects                                                             & Yes            & Yes             & Yes             & Yes             \\
      city-industry fixed effects                                                             & Yes            & Yes             & Yes             & Yes             \\
      Observations                                                                            & 30,676         & 30,676          & 30,676          & 30,676          \\
      R$^{2}$                                                                                 & 0.851          & 0.851           & 0.851           & 0.851           \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city
    \end{tablenotes}
\end{table}

\hfill \break

%%% table 4
\begin{table}[!htbp] \centering
  \caption{Parallel trend}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{3}{c}{The Dependent variable: Ln SO2_{ikt}} \\
      \cline{2-4}
      \\[-1.8ex] & (1) & (2) & (3)\\
      \\[-1.8ex] & (All sample) & (TCZ) & (No TCZ)\\
      \\[-1.8ex] & (TCZ_i \times \text{Polluted}_k \times Year) & (Polluted_k \times Year) & (Polluted_k \times Year)\\
      \hline \\[-1.8ex]
      2003                        & $-$0.409       & $-$0.091       & 0.228   \\
                                  & (0.272)        & (0.115)        & (0.259) \\
      2004                        & $-$0.253       & $-$0.098       & 0.078   \\
                                  & (0.287)        & (0.112)        & (0.308) \\
      2005                        & $-$0.420       & $-$0.153       & 0.178   \\
                                  & (0.263)        & (0.127)        & (0.272) \\
      2006                        & $-$0.503$^{*}$ & $-$0.211       & 0.159   \\
                                  & (0.270)        & (0.129)        & (0.288) \\
      2007                        & $-$0.460       & $-$0.246$^{*}$ & 0.127   \\
                                  & (0.303)        & (0.145)        & (0.312) \\
      \hline \\[-1.8ex]
      City-year fixed effects     & Yes            & Yes            & Yes     \\
      Industry-year fixed effects & Yes            & No             & No      \\
      City-industry fixed effects & Yes            & Yes            & Yes     \\
      Observations                & 30,676         & 23,333         & 7,343   \\
      R$^{2}$                     & 0.851          & 0.827          & 0.861   \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

\hfill \break

%%%table 5
\begin{table}[!htbp] \centering
  \caption{Soft budget constraint as reflected in the SOEs’ reaction to the SPZs’ and coastal area’s policies in China}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\
      \cline{2-5}
      \\[-1.8ex] & (1) & (2) & (3) & (4)\\
      \hline \\[-1.8ex]
      TCZ_i \times \text{Period} \times \text{Polluted}_k                                         & $-$0.275$^{*}$ & $-$0.320$^{**}$ & $-$0.331$^{**}$ & $-$0.378$^{**}$ \\
                                                                                                  & (0.166)        & (0.145)         & (0.155)         & (0.160)         \\
      SPZ_i \times \text{Period} \times \text{Polluted}_k                                         & 0.081          & 0.070           & 0.004           & 0.019           \\
                                                                                                  & (0.158)        & (0.147)         & (0.155)         & (0.161)         \\
      Coastal_i \times \text{Period} \times \text{Polluted}_k                                     & $-$0.083       & $-$0.034        & $-$0.034        & $-$0.044        \\
                                                                                                  & (0.148)        & (0.150)         & (0.153)         & (0.161)         \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{count share SOE}_{k}       & 1.531          &                 &                 &                 \\
                                                                                                  & (1.185)        &                 &                 &                 \\
      SPZ_i \times \text{Period} \times \text{Polluted}_k \times \text{count share SOE}_{k}       & 0.181          &                 &                 &                 \\
                                                                                                  & (1.054)        &                 &                 &                 \\
      Coastal_i \times \text{Period} \times \text{Polluted}_k \times \text{count share SOE}_{k}   & 0.077          &                 &                 &                 \\
                                                                                                  & (1.091)        &                 &                 &                 \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{output share SOE}_{k}      &                & 1.305$^{*}$     &                 &                 \\
                                                                                                  &                & (0.749)         &                 &                 \\
      SPZ_i \times \text{Period} \times \text{Polluted}_k \times \text{output share SOE}_{k}      &                & 0.300           &                 &                 \\
                                                                                                  &                & (0.689)         &                 &                 \\
      Coastal_i \times \text{Period} \times \text{Polluted}_k \times \text{output share SOE}_{k}  &                & $-$0.327        &                 &                 \\
                                                                                                  &                & (0.774)         &                 &                 \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{capital share SOE}_{k}     &                &                 & 0.924           &                 \\
                                                                                                  &                &                 & (0.595)         &                 \\
      SPZ_i \times \text{Period} \times \text{Polluted}_k \times \text{capital share SOE}_{k}     &                &                 & 0.477           &                 \\
                                                                                                  &                &                 & (0.544)         &                 \\
      Coastal_i \times \text{Period} \times \text{Polluted}_k \times \text{capital share SOE}_{k} &                &                 & $-$0.150        &                 \\
                                                                                                  &                &                 & (0.559)         &                 \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{labour share SOE}_{k}      &                &                 &                 & 1.391$^{*}$     \\
                                                                                                  &                &                 &                 & (0.725)         \\
      SPZ_i \times \text{Period} \times \text{Polluted}_k \times \text{labour share SOE}_{k}      &                &                 &                 & 0.525           \\
                                                                                                  &                &                 &                 & (0.666)         \\
      Coastal_i \times \text{Period} \times \text{Polluted}_k \times \text{labour share SOE}_{k}  &                &                 &                 & $-$0.142        \\
                                                                                                  &                &                 &                 & (0.723)         \\
      \hline \\[-1.8ex]
      City-year fixed effects                                                                     & Yes            & Yes             & Yes             & Yes             \\
      Industry-year fixed effects                                                                 & Yes            & Yes             & Yes             & Yes             \\
      City-industry fixed effects                                                                 & Yes            & Yes             & Yes             & Yes             \\
      Observations                                                                                & 30,676         & 30,676          & 30,676          & 30,676          \\
      R$^{2}$                                                                                     & 0.851          & 0.851           & 0.851           & 0.852           \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

%%%table 6
\begin{table}[!htbp] \centering
  \caption{Environmental policy, Wealth and Population pressure}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\
      \cline{2-5}
      \\[-1.8ex] & (1) & (2) & (3) & (4)\\
      \hline \\[-1.8ex]
      \text{Polluted}_k \times \text{ln gdp per cap}_{it}                                    & $-$0.038 & $-$0.034        & $-$0.029        & $-$0.036        \\
                                                                                              & (0.297)  & (0.298)         & (0.298)         & (0.297)         \\
      \text{Polluted}_k \times \text{ln population}_{it}                                     & 0.165    & 0.170           & 0.172           & 0.172           \\
                                                                                              & (0.227)  & (0.228)         & (0.228)         & (0.228)         \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k                                     & $-$0.238 & $-$0.280$^{**}$ & $-$0.317$^{**}$ & $-$0.360$^{**}$ \\
                                                                                              & (0.153)  & (0.142)         & (0.151)         & (0.156)         \\
      TCZ_i \times \text{Period} \times \text{count share SOE}_{k}                            & $-$1.177 &                 &                 &                 \\
                                                                                              & (0.888)  &                 &                 &                 \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{count share SOE}_{k}   & 1.522    &                 &                 &                 \\
                                                                                              & (1.115)  &                 &                 &                 \\
      TCZ_i \times \text{Period} \times \text{output share SOE}_{k}                           &          & $-$0.842        &                 &                 \\
                                                                                              &          & (0.574)         &                 &                 \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{output share SOE}_{k}  &          & 1.327$^{*}$     &                 &                 \\
                                                                                              &          & (0.731)         &                 &                 \\
      TCZ_i \times \text{Period} \times \text{capital share SOE}_{k}                          &          &                 & $-$0.707        &                 \\
                                                                                              &          &                 & (0.438)         &                 \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{capital share SOE}_{k} &          &                 & 1.074$^{*}$     &                 \\
                                                                                              &          &                 & (0.577)         &                 \\
      TCZ_i \times \text{Period} \times \text{labour share SOE}_{k}                           &          &                 &                 & $-$1.044$^{*}$  \\
                                                                                              &          &                 &                 & (0.562)         \\
      TCZ_i \times \text{Period} \times \text{Polluted}_k \times \text{labour share SOE}_{k}  &          &                 &                 & 1.545$^{**}$    \\
                                                                                              &          &                 &                 & (0.709)         \\
      \hline \\[-1.8ex]
      City-year fixed effects                                                                 & Yes      & Yes             & Yes             & Yes             \\
      Industry-year fixed effects                                                             & Yes      & Yes             & Yes             & Yes             \\
      City-industry fixed effects                                                             & Yes      & Yes             & Yes             & Yes             \\
      Observations                                                                            & 30,195   & 30,195          & 30,195          & 30,195          \\
      R$^{2}$                                                                                 & 0.852    & 0.852           & 0.852           & 0.852           \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

\hfill \break

%%% table 7
\begin{table}[!htbp] \centering
  %\resizebox{1\textwidth}{!}{
    %\begin{threeparttable}
    \caption{State versus Private sectors}
      \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
     \label{}
      \begin{tabular}{lrrrr}
        \multicolumn{1}{l}{\textbf{Panel A: sectors dominated by SOEs}} \\
        \toprule
        & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\
        \cline{2-5}
        \\[-1.8ex] & (1) & (2) & (3) & (4)\\
        \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
        \hline \\[-1.8ex]
        TCZ_i \times \text{Polluted}_k \times \text{Period} & $-$0.123 & 0.101           & 0.114           & 0.235           \\
                                                            & (0.216)  & (0.234)         & (0.229)         & (0.232)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        Observations                                        & 9,232    & 9,824           & 10,423          & 10,076          \\
        Number sectors                                      & X        & 92              & 104             & 98              \\
        R$^{2}$                                             & 0.888    & 0.865           & 0.869           & 0.862           \\
        \bottomrule
        \\ %%% Create second table
        \multicolumn{1}{l}{\textbf{Panel B: sectors dominated by Private ownership}} \\
        \toprule
        & \multicolumn{4}{c}{The Dependent variable: Ln SO2_{ikt}} \\
        \cline{2-5}
        \\[-1.8ex] & (1) & (2) & (3) & (4)\\
        \\[-1.8ex] & (SOE count) & (Output share) & (Capital share) & (Labour share)\\
        \hline \\[-1.8ex]
        TCZ_i \times \text{Polluted}_k \times \text{Period} & $-$0.138 & $-$0.243$^{**}$ & $-$0.272$^{**}$ & $-$0.284$^{**}$ \\
                                                            & (0.145)  & (0.124)         & (0.124)         & (0.125)         \\
        \hline \\[-1.8ex]
        City-year fixed effects                             & Yes      & Yes             & Yes             & Yes             \\
        Industry-year fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        City-industry fixed effects                         & Yes      & Yes             & Yes             & Yes             \\
        Observations                                        & 21,444   & 20,852          & 20,253          & 20,600          \\
        Number sectors                                      & X        & 204             & 192             & 198             \\
        R$^{2}$                                             & 0.849    & 0.857           & 0.853           & 0.858           \\
    \end{tabular}
    \end{adjustbox}
    \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city
    \end{tablenotes}
\end{table}

\hfill \break

%%%Table 8
\begin{table}[!htbp] \centering
  \caption{The effectiveness of TCY's policy-induced incentives to the bureaucrats}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{2}{c}{The Dependent variable: Ln SO2_{ikt}} \\
      \cline{2-3}
      \\[-1.8ex] & (1) & (2)\\
      \\[-1.8ex] & (TCZ) & (No TCZ)\\
      \hline \\[-1.8ex]
      \text{Period} \times \text{target}_i \times \text{Polluted}_k & $-$0.413$^{***}$ & $-$1.415 \\
                                                             & (0.141)          & (1.672)  \\
      \hline \\[-1.8ex]
      City-year fixed effects                                & Yes              & Yes      \\
      Industry-year fixed effects                            & Yes              & Yes      \\
      City-industry fixed effects                            & Yes              & Yes      \\
      Observations                                           & 23,333           & 7,343    \\
      R$^{2}$                                                & 0.847            & 0.892    \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

\hfill \break

%%%Table 9
\begin{table}[!htbp] \centering
  \caption{Fighting against pollution via productivity improvement: SOEs versus private firms}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{}
    \begin{tabular}{@{\extracolsep{5pt}}lcccccccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{5}{c}{The Dependent variable:} \\
      \\[-1.8ex] & (SOE) & (PRIVATE) & (SOE) & (PRIVATE) & (SOE) & (PRIVATE) & (SOE) & (PRIVATE)\\
      \\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\
      \cline{2-8}
      TCZ_c \times \text{Polluted}_i \times \text{Period}     & 0.506$^{**}$ & 0.536$^{***}$ &               &               &               &               & 0.005         & 0.345$^{***}$ \\
                                                              & (0.205)      & (0.023)       &               &               &               &               & (0.213)       & (0.111)       \\
      SPZ_c \times \text{Polluted}_i \times \text{Period}     &              &               & 0.070$^{***}$ & 0.147$^{***}$ &               &               & 0.070$^{***}$ & 0.147$^{***}$ \\
                                                              &              &               & (0.016)       & (0.001)       &               &               & (0.016)       & (0.001)       \\
      Coastal_c \times \text{Polluted}_i \times \text{Period} &              &               &               &               & 0.513$^{***}$ & 0.382$^{***}$ & 0.510$^{***}$ & 0.191$^{*}$   \\
                                                              &              &               &               &               & (0.159)       & (0.116)       & (0.171)       & (0.112)       \\
      \hline \\[-1.8ex]
      City-year fixed effects                                 & Yes          & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           \\
      Industry-year fixed effects                             & Yes          & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           \\
      City-industry fixed effects                             & Yes          & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           \\
      Observations                                            & 2,415        & 34,437        & 2,415         & 34,437        & 2,415         & 34,437        & 2,415         & 34,437        \\
      R$^{2}$                                                 & 0.482        & 0.104         & 0.481         & 0.103         & 0.482         & 0.104         & 0.482         & 0.104         \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

>>>>

\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{booktabs,caption,threeparttable, siunitx, adjustbox}

@@

\begin{table}[!htbp] \centering
  \caption{Fighting against pollution via productivity improvement: SOEs versus private firms}
  \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
    \label{eq:tfp}
    \begin{tabular}{@{\extracolsep{5pt}}lcccccccc}
      \\[-1.8ex]\hline
      \hline \\[-1.8ex]
      & \multicolumn{5}{c}{The Dependent variable:} \\
      \\[-1.8ex] & (SOE) & (PRIVATE) & (SOE) & (PRIVATE) & (SOE) & (PRIVATE) & (SOE) & (PRIVATE)\\
      \\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\
      \cline{2-8}
      TCZ_c \times \text{Polluted}_i \times \text{Period}     & 0.506$^{**}$ & 0.536$^{***}$ &               &               &               &               & 0.005         & 0.345$^{***}$ \\
                                                              & (0.205)      & (0.023)       &               &               &               &               & (0.213)       & (0.111)       \\
      SPZ_c \times \text{Polluted}_i \times \text{Period}     &              &               & 0.070$^{***}$ & 0.147$^{***}$ &               &               & 0.070$^{***}$ & 0.147$^{***}$ \\
                                                              &              &               & (0.016)       & (0.001)       &               &               & (0.016)       & (0.001)       \\
      Coastal_c \times \text{Polluted}_i \times \text{Period} &              &               &               &               & 0.513$^{***}$ & 0.382$^{***}$ & 0.510$^{***}$ & 0.191$^{*}$   \\
                                                              &              &               &               &               & (0.159)       & (0.116)       & (0.171)       & (0.112)       \\
      \hline \\[-1.8ex]
      City-year fixed effects                                 & Yes          & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           \\
      Industry-year fixed effects                             & Yes          & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           \\
      City-industry fixed effects                             & Yes          & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           & Yes           \\
      Observations                                            & 2,415        & 34,437        & 2,415         & 34,437        & 2,415         & 34,437        & 2,415         & 34,437        \\
      R$^{2}$                                                 & 0.482        & 0.104         & 0.481         & 0.103         & 0.482         & 0.104         & 0.482         & 0.104         \\
      \hline
      \hline \\[-1.8ex]
      \end{tabular}
  \end{adjustbox}
  \begin{tablenotes}
      \small
      \item 
      Note: $^{*}$p$<$0.1 $^{**}$p$<$0.05 $^{***}$p$<$0.01 \\
      Heteroskedastiikty-robust standard errors in parentheses are clustered by city \\
    \end{tablenotes}
\end{table}

### 2020-04-27 Temp_tables/Tables_paper/02_paper_version_2/07_DC_TFP_Coastal.tex
back up before new paper

\begin{document}% Date and time \times Sun, Apr 26, 2020 - 11:08:20
\begin{table}[!htbp] \centering 
  \caption{\\ Industrial concentration and environmental regulation effectiveness} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{Dependent variable \text { SO2 emission }_{i k t}} \\ 
\cline{2-5}

\\[-1.8ex]
            &\multicolumn{2}{c}{Concentrated}&\multicolumn{2}{c}{No Concentrated}\\
\\[-1.8ex] & (1) & (2) & (3) & (4)\\ 
\hline \\[-1.8ex] 
   target_c \times \text{Period}  & $-$0.156 &  & 0.012 &  \\ 
  & (0.323) &   & (0.104) &   \\ 
   target_c \times \text{Polluted}_i  & 0.532 &  & 0.411$^{***}$ &  \\ 
  & (0.351) &   & (0.145) &   \\ 
   target_c \times \text{Period} \times \text{Polluted}_i  & $-$0.074 & 0.208 & $-$0.302$^{**}$ & $-$0.504$^{***}$ \\ 
  & (0.392) & (0.396) & (0.153) & (0.143) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & No & Yes & No \\ 
Industry fixed effects & Yes & No & Yes & No \\ 
Year fixed effects & Yes & No & Yes & No \\ 
City-year fixed effects & No & Yes & No & Yes \\ 
Industry-year fixed effects & No & Yes & No & Yes \\ 
City-industry fixed effects & No & Yes & No & Yes \\ 
Observations & 9,181 & 9,181 & 21,495 & 21,495 \\ 
R$^{2}$ & 0.406 & 0.888 & 0.342 & 0.846 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1 and 3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Fri, Apr 24, 2020 - 16:14:21
\begin{table}[!htbp] \centering 
  \caption{Reduction mandate and TFP: Coastal  versus non - Coastal } 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{Dependent variable \text { TFP }_{fikt}} \\ 
\cline{2-5}

\\[-1.8ex]
            &\multicolumn{2}{c}{SOE}&\multicolumn{2}{c}{PRIVATE}\\
\\[-1.8ex] & (1) & (2) & (3) & (4)\\
 \\[-1.8ex]&  Coastal_c  & NO  Coastal_c  &  Coastal_c  & NO  Coastal_c \\
 \hline \\[-1.8ex] 
   target_c \times \text{Period} \times \text{Polluted}_i  & 0.158$^{**}$ & 0.119 & $-$0.012 & $-$0.087$^{**}$ \\ 
  & (0.063) & (0.098) & (0.023) & (0.036) \\ 
 \hline \\[-1.8ex] 
Firm & Yes & Yes & Yes & Yes \\ 
City-industry & Yes & Yes & Yes & Yes \\ 
City-time & Yes & Yes & Yes & Yes \\ 
time-industry & Yes & Yes & Yes & Yes \\ 
Observations & 19,540 & 21,948 & 477,084 & 130,225 \\ 
R$^{2}$ & 0.955 & 0.956 & 0.857 & 0.878 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}
